\documentclass[11pt]{article}
\usepackage[a4paper,top=2cm,bottom=2cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}
\usepackage{titling}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{etaremune}

\usepackage[english]{babel}
\usepackage{kotex}
\usepackage[round]{natbib}
\usepackage{bibentry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{framed}
\usepackage{ragged2e}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\usepackage[pro]{fontawesome5}



% \pagestyle{fancy}
% \fancyhf{}
% \rhead{2021-29298 Hyeonguk Bahk}
% \lhead{Final}
% \chead{}
% \renewcommand{\headrulewidth}{0pt}
\cfoot{\thepage}

\title{Curriculum Vitae}
\author{Hyeonguk Bahk}
\date{April 2024}

\begin{document}
\nobibliography{main}

  \setlength\parindent{0pt}
    \begin{minipage}{1\textwidth}
      \raggedright
      \textsc{Last Updated: \today}
    \end{minipage}

\vspace{15pt}

\begin{center}
{\Large\textsf{\textbf{Hyeonguk Bahk}}}

\vspace{3pt}
\textsf{\textbf{Curriculum Vitae}}

\end{center}

{\small {\footnotesize \faMapMarker*} Seoul National University $|$ {\footnotesize \faEnvelope} bahkhyeonguk@gmail.com $|$ {\footnotesize \faHome} hbahk.github.io $|$ {\scriptsize \faTag} 박형욱 / Hyeonguk Park}

\vspace{15pt}

\textbf{\large \textsf{Research Interests}}
\vspace{3pt}
\hrule
\begin{multicols}{2}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Formation and Evolution of Galaxy Clusters
    \item Observational Cosmology
    \item Dynamics of Galaxy Clusters
    \item Galaxy Redshift Survey and Instruments
    \item Active Galactic Nuclei and Supermassive Blackhole
\end{itemize}
\end{multicols}

\textbf{\large \textsf{Educations}}
\vspace{3pt}
\hrule

% \def\defaultleftmargin{20ex}
% \def\defaultitemindent{0ex}
\begin{itemize}[leftmargin=115pt]
    \item[\textbf{2021.09 -- Present:}] Ph.D. student in Astronomy, Seoul National University, Korea (Advisor: Prof. Ho Seong Hwang)
    \item[\textbf{2015.03 -- 2021.08:}] B.S. in Astronomy, Seoul National University, Korea.
\end{itemize}

\textbf{\large \textsf{Fellowship \& Scholarships}}
\vspace{3pt}
\hrule
\begin{itemize}[leftmargin=115pt, noitemsep]
    \item[\textbf{2024.03 -- Present:}] Next-Generation Scholar Fellowship, Seoul National University.
    \item[\textbf{2023.09 -- 2024.02:}] Brain Korea 21 (BK21), Korea Research Foundation.
    \item[\textbf{2022.03 -- 2023.08:}] Graduate Student Instructor (GSI) Scholarship, Seoul National University.
    \item[\textbf{2021.09 -- 2022.02:}] Brain Korea 21 (BK21), Korea Research Foundation.
    \item[\textbf{2015.03 -- 2021.08:}] Yongwoon Scholarship, Yongwoon Scholarship Foundation.
\end{itemize}


\textbf{\large \textsf{Teaching Experience}}
\vspace{3pt}
\hrule
\begin{itemize}[leftmargin=115pt, noitemsep]
    \item[\textbf{2023.03 -- Present:}] Teaching Assistant, Techniques in Astronomical Observation (graduate course), Seoul National University.
    \item[\textbf{2021.09 -- 2022.12:}] Teaching Assistant, Astronomical Observation and Lab (undergraduate course), Seoul National University.
\end{itemize}


\textbf{\large \textsf{Service \& Community Outreach}}
\vspace{3pt}
\hrule
\begin{itemize}[leftmargin=115pt, noitemsep]
    \item[\textbf{2022.09 -- 2023.05:}] Scientific Reviewer, FUNdamental SCIence LECture (FunSciLec) Project, Knowledge Awakening On Stage (KAOS) Foundation.
    \item[\textbf{2022.05 -- 2023.02:}] Editorial Team Member and Scientific Reviewer, K-MOOC Astronomy Program, Seoul National University.
    \item[2019 Apr -- 2020 Nov:] Military Service (112 Strike Force, Auxiliary Police).
\end{itemize}


\textbf{\large \textsf{Publications}}
\vspace{3pt}
\hrule

\begin{etaremune}
    \item \bibentry{bahk24}
    \item \bibentry{shin21}
    \item \bibentry{bahk19}
\end{etaremune}

% \bibliography{main}
\bibliographystyle{abbrvnat}

\end{document}
